Quantifying Directionality and Innovation Output in Sweden's Transition to a Forest-Based Bioeconomy

### 2024-09-11 20240906-pjk-NEST.qmd
update nest presentation

@@

2. [Positive directionality towards bioresource vision]{.text-royal-blue-600}, but overlap between visions and open development paths

>>>>

::: {.columns}
::: {.column width=66%}

@@

2. [Positive directionality towards bioresource vision]{.text-royal-blue-600}, but overlap between visions and open development paths
:::
::: {.column width=33%}

**Get the Paper**

{{< qrcode https://pjkreutzer.github.io/files/2024-05-05_pjk_draft_directionality.pdf width=100 height=100 colorDark='#0011bb' >}}
:::
:::
